Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
Improve validity threats

A threat to the internal validity of our experiment could be the false alarms of the
FindBugs tool. False positives and negatives of static analysis tools and
how they can be reduced is an issue that has already been discussed in literature (see
Section~\ref{sec:rel}). Furthermore, consider the case where a
security bug is reported, but it is invalidated based on the context of the
application. For instance, an {\sc sql} injection vulnerability~\cite{RL12}
in an application that requires no external input could be reported by FindBugs,
but in this case would be a false positive alarm.

We also have to mention that our analysis is done on projects written in the
Java programming language. Hence, a threat to the external validity of our work
is the fact that our results may not be the same in another programming
environment.

>>>>

A threat to the internal validity of our experiment could be the false alarms of the
FindBugs tool. False positives and negatives of static analysis tools and
how they can be reduced is an issue that has already been discussed in the literature
(see Section~\ref{sec:rel}).
In addition, reported security bugs may not be applicable to an
application's typical use context.
For instance, FindBugs could report an {\sc sql} injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false positive alarm.

Furthermore, given that our analysis is done on open-source projects
written in the Java programming language and hosted on Maven,
a threat to the external validity of our work
is the fact that our results may not be applicable to other
programming languages, ecosystems, and development cultures.
